|

### 2021-12-30 text/ManuscriptDraft.Rmd
Small manuscript update

---
new_session: FALSE
title: |
  **Monitoring the phenology of individual flowers using deep learning and automatic tracking**
author:
- Hjalte M. R. Mann
- Alexandros Iosifidis
- Toke T. Høye
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
  html_document:
    df_print: paged
fontfamily: mathpazo
fontsize: 12pt
geometry: margin = 1in
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{dcolumn}
- \usepackage{caption}
- \usepackage{float}
- \usepackage{afterpage}
- \usepackage{siunitx}
- \usepackage{amsmath}
keywords: Tracking, flowering phenology, Arctic, 
bibliography: ./library.bib
csl: ./journal-of-ecology.csl
abstract: ABSTRACT | Often simple variables will be used to describe the flowering phenology of a population of plants, e.g. onset or peak of flowering and to infer respones to climate change. Here we show that image-based monitoring of field plots at very high temporal resolution can return information on flowering phenology at the level of indiviuals. Further, we present an automatic flower tracking algorithm.
---

@@

>>>>

---
new_session: FALSE
title: |
  **Monitoring the phenology of individual flowers using deep learning and automatic tracking**
author:
- Hjalte M. R. Mann
- Alexandros Iosifidis
- Toke T. Høye
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
  html_document:
    df_print: paged
fontfamily: mathpazo
fontsize: 12pt
geometry: margin = 1in
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{dcolumn}
- \usepackage{caption}
- \usepackage{float}
- \usepackage{afterpage}
- \usepackage{siunitx}
- \usepackage{amsmath}
keywords: Tracking, flowering phenology, Arctic, 
bibliography: ./library.bib
csl: ./journal-of-ecology.csl
abstract: ABSTRACT | Often simple variables will be used to describe the flowering phenology of a population of plants, e.g. onset or peak of flowering. Here we show that image-based monitoring of field plots at very high temporal resolution can return information on flowering phenology at the level of indiviuals. Further, we present a framework for automatically tracking, filtering, and visualizing flowers in time-lapse image series. We compare the results of automatic tracking with manual tracking. 
---

@@

To estimate the optimal values for max_disappeared and max_distance, we analysed the ground truth tracks of the four series.

To estimate the value for max_distance, we calculated the largest distance between any two points within any track for any flower in each of the four series.

The maximum number of frames a flower track was lost and subsequently reappeared were xxx.
